---
title: "InteractionPlot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{InteractionPlot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```





Nicole Wang

In recent years, various plotting packages have become well-known in R for data visualization, with tools like ggplot2 commonly used for descriptive analysis. While many of these tools handle tasks like displaying frequency plots or density charts, meeting most users' needs, there's a noticeable gap when it comes to visualizing data containing interaction effects. These interaction effects graphics are crucial, especially in fields like social science and public health. Many social science researchers opt for binary variables because they're straightforward to interpret. The challenge arises when they need to explore all potential interaction terms across hundreds of variables. Our goal is to address two main issues: identifying significant interaction effects between binary variables in logistics regression and creating automatic visualizations of the findings.

Interaction effects stand apart from other variables that you can measure directly. They need to be inferred indirectly through an interaction term in statistics model. Our package plans to streamline this process. We start by having the model $Y_{i,j}=X_1...+X_n+X_i*X_j$, for i,j=1..n. We'll need users to specify the response variable first. Based on this, we'll filter out all non-binary variables and create a matrix to hold all combinations of interaction variables, helping to cut down on computing costs. We'll then apply linear regression analysis to the data and highlight the significant interaction terms. Lastly, we'll take these insights and generate visualizations automatically with description of i number in main label, making it easier for users to understand the interaction effects in their data.



## Usage

To install InteractionPlot package, copy and paste the following code into your console:

```{r}
library(InteractionPlot)
```

## Example & Analysis
### In vignette file, we will do full data analysis analysis for example 1 (simulation)

### Example 1 -- Simulation example

##### set v1, v2, v3, v5 as binary, v4 and y as continous.

##### set 2 interaction effect, v2 * v3 and v1 * v3.

##### We generate y by setting different weight for variables and interaction terms and add them together.

```{r}
set.seed(1234)

n <- 100 
v1 = rbinom(n, 1, 0.4)
v2 <- rbinom(n, 1, 0.5)  
v3 <- rbinom(n, 1, 0.6)  
v4 = rnorm(n)
v5 = rbinom(n, 1, 0.6)
interaction_effect1 <- v2 * v3 
interaction_effect2 <- v1 * v3 

y <- 2 * v1 + 2 * v2 + 2 * v3 + 200 * interaction_effect1 + 200 * interaction_effect2 + rnorm(n,mean=0,sd=1)  

data <- data.frame(y = y, v1 = v1, v2 = v2, v3 = v3, v4 = v4, v5 = v5)

```

#### Step 1 : Data Cleaning and Preparation

##### keep y, and filter out continous variables (v4 in this case) 

##### construct a matrix for names of interaction item for reducing computing works

```{r}
prepared_data <- prepare_data(data, "y")
print(head(prepared_data))

interaction_matrix <- create_interaction_matrix(prepared_data, "y")
print(head(interaction_matrix))
```

#### Step 2 : Fit Regression Model and Extract Significant Interactions

##### The model will fit for each interaction term, for example, (in this case v4 was removed because it's continuous)

##### y = v1 + v2 + v3 + v5 + v1 * v2

##### y = v1 + v2 + v3 + v5 + v1 * v3

##### y = v1 + v2 + v3 + v5 + v2 * v3,....etc

##### We may see some terms are missing in full_results because of their p-value is NA 

```{r}
full_results <- analyze_interactions(prepared_data, interaction_matrix, "y")
print(full_results)
significant_interactions <- extract_significant(full_results)
print(significant_interactions)
```

##### Analysis: 

##### According to full results, summary for all possible models are listed. 

##### After extracting significant interaction, we can see v1 * v3 and v2 * v3 are significant (p < 0.05),

#### The result is the same as what we are setting in simulation.

#### Step 3 : Generate Final Regression

##### final model: y = v1 + v2 + v3 + v1 * v3 + v2 * v3

```{r}
fit_final_regression <- final_regression(prepared_data, "y")
fit_final_regression
```

##### Analysis: 

##### After fitting final mode, we can see v1 * v3 and v2 * v3 are significant (p < 0.05).

##### Estimates for each terms are similar to what we set in simulation. 

##### It is slightly different from original weights because we add noise when we are generating y.

##### Adjusted-R^2 = 99.99%, P for final model < 0.05, good model.

#### Step 4 : Plot Interaction Effects

##### 2 plots of interaction v1*v3 (each variable has opportunity to be putted on the  x-axis)

##### 2 plots of interaction v2*v3 (each variable has opportunity to be putted on the  x-axis)


```{r}
library(dplyr)
library(ggplot2)
plots <- plot_interaction_effects(prepared_data, "y", significant_interactions)
plots
```

##### Analysis:

##### second plot (v1,v3 when v3 on x-axis) and fourth (v2,v3 when v3 on x-axis) are better plots than the rests

##### the mean value of y for v1 and v2 depends on the category of v3. When v3 = 1, the the mean y of v2 = 1 (around 300) larger much more that of v2=0 (less than 100).

#### In conclusion,

#### In addition to linear regression summary, interaction plots also helps people to understand the interaction effects.

